Software reliability: Experiences\\ in European scientific research\\ projects and new trends

### 2017-11-08 paper.tex

\author{D.C. Duma, %~\IEEEmembership{Member,~IEEE,}
        E. Ronchieri, %~\IEEEmembership{Fellow,~OSA,}
        P. Orviz Fernandez, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        M. David, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        J. Gomes, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        D. Salomoni, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{D. C. Duma, E. Ronchieri, and D. Salomoni are with INFN - CNAF, Bologna, Italy.}%
\thanks{P. Orviz Fernandez, is with CSIC, Santander, Spain, (e-mail: orviz@ifca.unican.es)}%
\thanks{M. David, and J. Gomes are with LIP, Lisbon, Portugal}%
}

@@

\begin{abstract}
In this work we describe the trends in scientific software reliability by analyzing past European Commission funded software development projects in the context of distributed computing field such as Enabling Grids for E-sciencE and European Middleware Initiative, and the ongoing INDIGO-DataCloud.
\end{abstract}

>>>>

\author{D.C. Duma, %~\IEEEmembership{Member,~IEEE,}
        E. Ronchieri, %~\IEEEmembership{Fellow,~OSA,}
        P. Orviz Fernandez, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        M. David, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        J. Gomes, %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
        D. Salomoni %~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{D. C. Duma, E. Ronchieri, and D. Salomoni are with INFN - CNAF, Bologna, Italy.}%
\thanks{P. Orviz Fernandez, is with CSIC, Santander, Spain, (e-mail: orviz@ifca.unican.es)}%
\thanks{M. David, and J. Gomes are with LIP, Lisbon, Portugal}%
}

@@

\begin{abstract}
In this work we describe the trends in scientific software reliability by analyzing past European Commission funded software development projects in the context of distributed computing field, such as Enabling Grids for E-sciencE, European Middleware Initiative and the ongoing INDIGO-DataCloud.
\end{abstract}
